Supplementary Materials for Differences in the Risk of Grade Retention for Biracial and Monoracial Students in the US, 2010-2019

### 2023-03-13 products/paper/supp_materials.qmd
Add figure to supplementary appendix to address issue #34

```{r}
#| label: setup
#| include: false
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","bic_spec_tests.RData"))
load(here("analysis","output","model_summaries.RData"))
load(here("analysis","output","marg_prob_alt.RData"))
load(here("analysis","output","acs.RData"))
```

@@

>>>>

```{r}
#| label: setup
#| include: false
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","bic_spec_tests.RData"))
load(here("analysis","output","model_summaries.RData"))
load(here("analysis","output","marg_prob_alt.RData"))
load(here("analysis","output","models_grade_robust.RData"))
load(here("analysis","output","acs.RData"))
color_choices <- c("#003f5c","#58508d","#bc5090","#ff6361","#000000","#ffa600")
```

@@

```{r}
#| label: fig-results-grade-group
#| fig-cap: Probability of being clearly behind expected grade for biracial respondents, in comparison to their monoracial comparison groups, separately by elementary (not including kindergarten), middle school, and high school. Non-overlap in color corresponding confidence bands indicates statistically significant difference at the 5% level, Baseline model includes year, grade, location, and state fixed effects. Full models include control variables for nativity, English proficiency, income, education, home ownership, and marital status of parents.
#| fig-height: 7.1
coef_table <- results_elem$coef_table %>%
  mutate(model="elementary")
coef_table <- results_middle$coef_table %>%
  mutate(model="middle school") %>%
  bind_rows(coef_table)
coef_table <- results_hs$coef_table %>%
  mutate(model="high school") %>%
  bind_rows(coef_table) %>%
  mutate(model=factor(model, levels=c("elementary","middle school",
                                      "high school")),
         mrace=factor(mrace, levels=c("Black/White",
                                      "Black/Latino",
                                      "Black/Asian",
                                      "Black/Indigenous",
                                      "White/Indigenous",
                                      "White/Latino",
                                      "White/Asian",
                                      "Latino/Asian",
                                      "Indigenous/Latino",
                                      "Indigenous/Asian")))

ci_df <- results_elem$ci_df %>%
  mutate(model="elementary")
ci_df <- results_middle$ci_df %>%
  mutate(model="middle school") %>%
  bind_rows(ci_df)
ci_df <- results_hs$ci_df %>%
  mutate(model="high school") %>%
  bind_rows(ci_df) %>%
  mutate(model=factor(model, levels=c("elementary","middle school",
                                      "high school")),
         mrace=factor(mrace, levels=c("Black/White",
                                      "Black/Latino",
                                      "Black/Asian",
                                      "Black/Indigenous",
                                      "White/Indigenous",
                                      "White/Latino",
                                      "White/Asian",
                                      "Latino/Asian",
                                      "Indigenous/Latino",
                                      "Indigenous/Asian")))

ggplot(coef_table, aes(x=term, y=estimate, color=colors))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=lower, ymax=upper, fill=colors), 
            color=NA, alpha=0.5)+
  geom_linerange(data=ci_df, 
                 position=position_dodge2(width = 0.1), size=1, alpha=0.5,
                 aes(ymin=lower, ymax=upper, color=colors))+
  geom_point()+
  coord_flip()+
  facet_grid(mrace~model, scales="free_y")+
  theme_bw()+
  theme(legend.position = "none", panel.grid = element_blank(), 
        strip.text.y = element_text(size = 4))+
  scale_color_manual(values=color_choices)+
  scale_fill_manual(values=color_choices)+
  scale_y_continuous(labels = scales::percent)+
  labs(x=NULL,
       y="average adjusted predicted probability of being behind expected grade")
```
